\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-05-20 manuscript.tex
Formatting
Formatted title and footnote pages, see space for acknowledgements

\documentclass[11pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\usepackage[leftcaption]{sidecap}
\sidecaptionvpos{figure}{c} %position side caption
\usepackage{lineno}
\usepackage{color}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}  
%\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\usepackage[table]{xcolor} %for table line color alteration
\usepackage{subscript}
\renewcommand{\baselinestretch}{1.5}
\bibliographystyle{AJB}

@@

@@

\title{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}

\author[1]{Laura Vann}
\author[1,2]{Thomas Kono}
\author[1,3]{Tanja Pyh\"aj\"arvi}
\author[1,4]{Matthew B. Hufford\thanks{mhufford@iastate.edu}}
\author[1,5]{Jeffrey Ross-Ibarra\thanks{rossibarra@ucdavis.edu}}
\affil[1]{Department of Plant Sciences, University of California Davis}
\affil[2]{Department of Agronomy and Plant Genetics, University of Minnesota Twin Cities}
\affil[3]{Department of Biology, University of Oulu}
\affil[4]{Department of Ecology, Evolution, and Organismal Biology, Iowa State University}
\affil[5]{Center for Population Biology and Genome Center, University of California Davis}

@@

\maketitle

>>>>

\documentclass[11pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\usepackage[leftcaption]{sidecap}
\sidecaptionvpos{figure}{c} %position side caption
\usepackage{lineno}
\usepackage{lipsum}
\usepackage{color}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}  
%\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\usepackage[table]{xcolor} %for table line color alteration
\usepackage{subscript}
\renewcommand{\baselinestretch}{1.5}
\bibliographystyle{AJB}

@@

\makeatletter
\renewcommand{\maketitle}{\bgroup\vspace*{1cm}\setlength{\parindent}{0pt}
\begin{center}
  \textbf{\@title}

  \@author
\end{center}\egroup
}
\makeatother

\title{\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark}

\author[2]{Laura Vann}
\author[2,3]{Thomas Kono}
\author[2,4]{Tanja Pyh\"aj\"arvi}
\author[2,5,7]{Matthew B. Hufford}
\author[2,6,7]{Jeffrey Ross-Ibarra}
\affil[2]{Department of Plant Sciences, University of California Davis}
\affil[3]{Department of Agronomy and Plant Genetics, University of Minnesota Twin Cities}
\affil[4]{Department of Biology, University of Oulu}
\affil[5]{Department of Ecology, Evolution, and Organismal Biology, Iowa State University}
\affil[6]{Center for Population Biology and Genome Center, University of California Davis}
\affil[7]{Author for Correspondence}
\date{}

@@

\flushleft{\large{Vann \emph{et al.}: Variation in teosinte at the \emph{tb1} locus}

{\let\newpage\relax\maketitle}

@@

\clearpage
\footnotetext{\flushleft{Manuscript received \line(1,0){120};   revision accepted\line(1,0){120}.}
\vspace*{1cm}
\subsection*{Acknowledgements}
Place brief acknowledgments, if desired, as a separate paragraph, using the following style: “The author(s) thank(s)…”. For brevity, do not use first names. Include grant acknowledgments here.
}
\clearpage
